---
title: "STATS 250 Lab 3 Report"
author: "YOUR NAME GOES HERE IN QUOTES"
date: "TODAY'S DATE GOES HERE IN QUOTES"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
    css: assets/styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

Welcome to Lab 3! Complete the following exercises designed to help get you up and running in R and RStudio. It is important that you keep your answers inside the ".answer" blocks. Do NOT delete the three colon blocks (:::) and keep your responses between them. Use the tutorial for help, and feel free

Depending on your instruction method (synchronous or asynchronous), complete the following exercises collaboratively.

1.  **Synchronous remote:** You will be placed in a Zoom breakout room to work together in small groups.
2.  **Asynchronous remote:** Use Piazza for asynchronous collaboration.

**Collaborators:** If applicable, replace this text with the names of anyone you collaborated with on this project.

You can find a list of colors you can use in R [here](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf). You can also directly use RGB colors via the `rgb()` function (see the help for more), or hex codes. If you don't know what those are, stick to the named colors in the linked PDF.

# Lab Assignment

In this assignment, we'll be using a data set we will call `tuition` that contains information about cost of attendance for 1,861 colleges and universities around the United States.

## Question 1

::: {.question}
We'll start by reading in the data. The data are stored in a file called `tuition_cost.csv`. You'll need to give the name of this file (*in quotes!*) to `read.csv()`. When you read it in, call the data set `tuition`. **If you don't call it `tuition` you'll get errors later on.** Make sure you set `stringsAsFactors = TRUE`. 
:::

::: {.answer}
```{r question1, error = T}
# Replace this comment with code required for Question 1. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 2

::: {.question}
Before we make graphs or numerical summaries, give an overview of the data set in 2-3 sentences. Use whatever tools you like to preview the contents of the data. The goal is for you to understand what's going on in the data set before working with it. Include any code in the chunk below. (*Disclaimer: There's not a right or wrong answer here -- just explore.*) You might want to revisit functions used in labs 1 and 2.
:::

::: {.answer}
```{r question2, error = T}
# Replace this comment with code required for Question 2. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

Replace this text with your answer to Question 2.
:::

## Question 3

:::{.question}
 Make a boxplot of the variable which represents the total cost of attendance (room and board + tuition) for in-state students. Be sure to give it an appropriate title, axis labels, etc. Based on this boxplot, does it appear that the data are symmetric?
:::

:::{.answer}
```{r question3, error = T}
# Replace this comment with code required for Question 3. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

Replace this text with your answers to Question 3.

:::

## Question 4

:::{.question}
Make a histogram of the same variable from Question 3, being sure to include a proper title and axis labels. Play around with the `breaks` argument until you're satisfied with your histogram. Was your prediction about the symmetry of the data in Question 3 accurate? In the future, do you think it's always appropriate to describe shape based on a boxplot alone?
:::

:::{.answer}
```{r question4, error = T}
# Replace this comment with code required for Question 4. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

Replace this text with your answers to Question 4.

:::

## Question 5

:::{.question}
Make a side-by-side boxplot of the total cost of attendance for in-state students by type of institution (for profit / public / private). As always, be sure to provide an appropriate title and axis labels. In 1-2 sentences, describe what you see.
:::

:::{.answer}
```{r question5, error = T}
# Replace this comment with code required for Question 5. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

Replace this text with your answer to Question 5.

:::


## Question 6

:::{.question}
Does higher tuition mean higher living costs? Make a scatterplot of room and board costs vs. in-state tuition (remember we say "y vs. x", so room and board should be on the y axis). Color the points by institution type and include a legend. Write 1-2 sentences describing what you see.
:::

:::{.answer}
```{r question6, error = T}
# Replace this comment with code required for Question 6. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

Replace this text with your 1-2 sentence answer to Question 6

:::

## Question 7
:::{.question}
Subset the data to include only schools in Michigan and call the new subset `mi_tuition`. Using code, verify that your subset contains only Michigan schools.

*Hint:* Remember that computers are dumb, and you need to type things *exactly* as they are in the data.
:::

:::{.answer}
```{r question7, error = T}
# Replace this comment with code required for Question 7. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 8 
:::{.question}
Make a histogram of the variable you chose in Question 3 using `mi_tuition`. What do you notice about this histogram compared to the national histogram in Question 4?
:::

:::{.answer}
```{r question8, error = T}
# Replace this comment with code required for Question 8. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

Replace this text with your 1-2 sentence written answer to Question 8.

:::


# Wrap-Up and Submission

At the top of the document, make sure you've changed the `author` field to your name (in quotes!). If you'd like, change the date as well.

When you've finished the lab, click the **Knit** button one last time.

## Submission instructions

### If you're using RStudio Cloud

1.  In the Files pane, check the box next to `lab03-report.html`.
2.  Click More \> Export...
3.  Click Download and save the file on your computer in a folder you'll remember and be able to find later. You can just call the file `lab03report.html` or whatever else you'd like (as long as you remember what you called it).

### If you're using RStudio installed on your computer

1.  locate the `lab03-report.html` file on your computer. The file will be saved in the location indicated at the top of the files pane.

### Submission to Canvas

1.  Click the "Assignments" panel on the left side of the page. Scroll to find "Lab 3", and open the assignment. Click "Submit Assignment".
2.  Towards the bottom of the page, you'll be able to choose `lab03report.html` from the folder you saved it in from RStudio Cloud or noted if you're using RStudio Desktop. **You will only be able to upload a .html file -- do not upload any other file type.**
3.  Click "Submit Assignment". You're done!
